Binary companions of red giant stars in \apogee\ \DR

### 2018-03-02 paper/1-catalog/twoface-catalog.tex
high-K figures

\tablename~\ref{tbl:} contains a subset of the \apogee\ \DR\ \texttt{allStar}
catalog information for the stars that pass the above cut and therefore likely
have companions; For brevity below, we refer to this sample as the ``high-$K$''
stars, and the complimentary sample as the ``low-$K$'' stars.
\figurename~\ref{fig:highK} shows eight examples of high-$K$ stars, i.e. stars
that likely have companions, with different numbers of visits.
\figurename~\ref{fig:lowK} is the same for eight low-$K$ stars, i.e. stars that
either have no companions, low-mass companions, or companions at long periods or
high inclination.

@@

% % Notebook: "TODO"
% Should also include period-eccentricity panels with samples
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\textwidth]{highK}
% \end{center}
% \caption{%
% TODO
% \label{fig:highK}
% }
% \end{figure}

>>>>

\tablename~\ref{tbl:} contains a subset of the \apogee\ \DR\ \texttt{allStar}
catalog information for the stars that pass the above cut and therefore likely
have companions; For brevity below, we refer to this sample as the ``high-$K$''
stars, and the complimentary sample as the ``low-$K$'' stars.
\figurename s~\ref{fig:highK-0} and \ref{fig:highK-1} show eight examples of
high-$K$ stars, i.e. stars that likely have companions, with different numbers
of visits, $N$, indicated on the panels.
\figurename s~\ref{fig:lowK-0} and \ref{fig:lowK-1} is the same for eight
low-$K$ stars, i.e. stars that either have no companions, low-mass companions,
or companions at long periods or high inclination.

@@

% Notebook: "HighK"
\begin{figure}[hp]
\begin{center}
\includegraphics[width=\textwidth]{highK-0}
\end{center}
\caption{%
TODO
\label{fig:highK-0}
}
\end{figure}

\begin{figure}[hp]
\begin{center}
\includegraphics[width=\textwidth]{highK-1}
\end{center}
\caption{%
TODO
\label{fig:highK-1}
}
\end{figure}

\begin{figure}[hp]
\begin{center}
\includegraphics[width=\textwidth]{lowK-0}
\end{center}
\caption{%
TODO
\label{fig:lowK-0}
}
\end{figure}

\begin{figure}[hp]
\begin{center}
\includegraphics[width=\textwidth]{lowK-1}
\end{center}
\caption{%
TODO
\label{fig:lowK-1}
}
\end{figure}
